A Graph-based Framework for Coverage Analysis in Autonomous Driving

### 2025-10-05 article/article.tex
some parts in paper writing

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}

@@

CARLA (Car Learning to Act) is an open-source simulator specifically designed for autonomous driving research and development. It provides a highly realistic urban driving environment with diverse road layouts, weather conditions, and traffic scenarios. The simulator features a comprehensive sensor suite simulation, flexible API for scenario creation, and supports both learning-based and traditional autonomous driving approaches. CARLA enables researchers to test and validate autonomous vehicle systems in a safe, controllable environment before real-world deployment.

@@

\cite{Dosovitskiy17Carla}

>>>>

\documentclass{article}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{graphicx}

@@

CARLA (Car Learning to Act, \cite{Dosovitskiy17Carla}) is an open-source simulator specifically designed for autonomous driving research and 
development. It provides a highly realistic urban driving environment with 
diverse road layouts, weather conditions, and traffic scenarios. The simulator features a comprehensive 
sensor suite simulation, flexible API for scenario creation, and supports both learning-based 
and traditional autonomous driving approaches. CARLA enables researchers to test and 
validate autonomous vehicle systems in a safe, controllable environment before real-world deployment.

@@

Here, Carla version $0.9.15$ is used. The CARLA version $0.10.0$ is not used, because it had only 2 maps and
Mine\_1 (which is not really normal roads) at the start of this project.
Specifically, the following maps were used: Town01, Town02, Town03, Town04, Town05 and Town07. Plots
of these maps are shown in Figure \ref{fig:carla_maps}.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{plots/carla_maps_used.png}
\caption{Overview of CARLA maps used in the simulation study: Town01, Town02, Town03, Town04, Town05, and Town07. These maps provide diverse urban driving environments with varying road layouts, intersections, and traffic patterns.}
\label{fig:carla_maps}
\end{figure}

The data generation script implements sophisticated behavior control mechanisms to create 
diverse and realistic traffic scenarios. Multiple vehicle types including trucks, motorcycles, 
and regular cars are spawned with varying probabilities, each exhibiting different behavioral
characteristics such as speed preferences, following distances, and lane-changing tendencies. 
The script incorporates dynamic behavior modifications during simulation, including random slowdowns, 
periodic behavior changes, and adaptive responses to traffic conditions, resulting in rich and 
varied traffic scene data across multiple CARLA maps and simulation iterations. The simulation runs
have between 20 and 60 vehicles each.

The resulting data consists of xxx scenes with 11 seconds of simulation time each, in order to have a 
similar data size as the Argoverse 2.0 dataset.
